---
title: "Revision analysis tool with JDemetra+ version 3.x algorithms"
output: 
  html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Revision analysis tool with JDemetra+ version 3.x algorithms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author:
  - name: Corentin Lemasson
    url: https://github.com/clemasso
    affiliations:
        - name: NBB (National Bank of Belgium)
          country: Belgique
          city: Bruxelles
          url: "https://www.nbb.be/en"
    role: "Author"
  - name: Tanguy Barthelemy
    url: https://github.com/TanguyBarthelemy
    affiliations:
        - name: Insee
          country: France
          city: Paris
          url: "https://www.insee.fr/en/accueil"
    role: "Author"
abstract: Revision analyses provides important information on the efficiency of preliminary estimates, allowing to identify potential issues and/or improvements that could be made in the compilation process. This package provides a tool to automatically perform a battery of relevant tests on revisions and submit a visual report including both the main results and their interpretation. The tool can perform analysis on different types of revision intervals and on different vintage views.  
---

```{r setup vignette, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    eval = FALSE,
    comment = "#>"
)
```

# Introduction

This package performs revision analysis and offers both detailed and summary output including the generation of a visual report. It is composed on a selection of parametric tests which enable the users to detect potential bias (both mean and regression bias) and other sources of inefficiency in preliminary estimates. What we mean by inefficiency in preliminary estimates is whether further revisions are predictable in some way. 

This package uses the efficient libraries of [JDemetra+ v3](https://github.com/jdemetra/jdplus-main). It was built mostly based on Eurostat’s technical reports from D. Ares and L. Pitton (2013).
 
The next section helps with the installation of the package. The third section describes how to use the tool and give some important details on the main functions. In particular, it is important to mention beforehand that your input data must first be set in a specific format described in the sub-section on the [input data](#input_format). The fourth section is theoretical and describes each test being performed by the main function `revision_analysis()` (they could also be performed individually) and how to interpret them. Finally, you will find out all the reference papers in the last section.         

# Installation settings

This package relies on the Java libraries of [JDemetra+ v3](https://github.com/jdemetra/jdplus-main) and on the package [rjd3toolkit](https://github.com/rjdverse/rjd3toolkit) of [rjdverse](https://github.com/rjdverse). Prior the installation, you must ensure to have a Java version >= 17.0 on your computer. If you need to use a portable version of Java to fill this request, you can follow the instructions in the [installation manual](https://github.com/rjdverse/rjdemetra/wiki/Installation-manual) of RJDemetra.

In addition to a Java version >= 17.0, you must have a recent version of the R packages rJava (>= 1.0.6) and RProtobuf (>=0.4.17) that you can download from CRAN. Depending on your current version of R, you might also need to install another version of Rtools. (>= 3.6). 

This package also depends on the package [rjd3toolkit](https://github.com/rjdverse/rjd3toolkit) that you must install from GitHub prior to [rjd3revsions](https://github.com/rjdverse/rjd3revisions).

```{r package installation, echo = TRUE, eval = FALSE}
remotes::install_github("rjdverse/rjd3toolkit@*release")
remotes::install_github("rjdverse/rjd3revisions@*release", build_vignettes = TRUE)
```

Note that depending on the R packages that are already installed on your computer, you might also be asked to install or re-install a few other packages from CRAN. 

Finally, this package also suggests the R packages `formattable` and `kableExtra` (and `readxl` if you import your input data from Excel) downloadable from CRAN. You are invited to install them for an enhanced formatting of the output (i.e., meaningful colors). 

# Usage


## Input data {#input_format}

Your input data must be in a specific format: long, vertical or diagonal   as shown in one of the table below. Regarding the dates, the format shown in the examples below is acceptable, as are the other common date formats for both revision dates and time periods. Note that missing values can either be mentioned as NA (as in the example below) or not be included in the input at the best convenience of the user. 

### Format 1: long view

| rev_date    | time_period | obs_values  |
| ----------- | ----------- | ----------- |
| 2022-07-31  | 2022Q1      | 0.8         |
| 2022-07-31  | 2022Q2      | 0.2         |
| 2022-07-31  | 2022Q3      | NA          |
| 2022-07-31  | 2022Q4      | NA          |
| 2022-08-31  | 2022Q1      | 0.8         |
| ...         | ...         | ...         |

### Format 2: vertical view

| Period   | 2023/03/31 | 2023/04/30 | 2023/05/31 |
| -------- | ---------- | ---------- | ---------- |
| 2022M01  | 15.2       | 15.1       | 15.0       |
| 2022M02  | 15.0       | 14.9       | 14.9       |
| ...      | ...        | ...        | ...        |
| 2023M01  | 13.0       | 13.1       | 13.2       |
| 2023M02  |            | 12.1       | 12.1       |
| 2023M03  |            |            | 12.3       |

### Format 3: horizontal view

| Period     | 2022M01 | 2022M02 | ...     | 2023M01 | 2023M02 | 2023M03 |
| ---------- | ------- | ------- | ------- | ------- | ------- | ------- |
| 2023/03/31 | 15.2    | 15.0    | ...     | 13.0    |         |         |
| 2023/04/30 | 15.1    | 14.9    | ...     | 13.1    | 12.1    |         |
| 2023/05/31 | 15.0    | 14.9    | ...     | 13.2    | 12.1    | 12.3    |


Depending on the location of your input data, you can use `create_vintages_from_xlsx()` or `create_vintages_from_csv()`, or the more generic function `create_vintages()` to create the vintages (see section [vintages & revisions](#vintages)) later on. If you plan to use the generic function, you'll first need to put your input data in a data.frame in R as in the example below.

```{r input format, echo = TRUE, eval = TRUE}
# Long format
long_view <- data.frame(
    rev_date = rep(x = c("2022-07-31", "2022-08-31", "2022-09-30", "2022-10-31",
                         "2022-11-30", "2022-12-31", "2023-01-31", "2023-02-28"),
                   each = 4L),
    time_period = rep(x = c("2022Q1", "2022Q2", "2022Q3", "2022Q4"), times = 8L),
    obs_values = c(
        .8, .2, NA, NA, .8, .1, NA, NA,
        .7, .1, NA, NA, .7, .2, .5, NA,
        .7, .2, .5, NA, .7, .3, .7, NA,
        .7, .2, .7, .4, .7, .3, .7, .3
    )
)
print(long_view)

# Horizontal format
horizontal_view <- matrix(data = c(.8, .8, .7, .7, .7, .7, .7, .7, .2, .1,
                                   .1, .2, .2, .3, .2, .3, NA, NA, NA, .5, .5, .7, .7,
                                   .7, NA, NA, NA, NA, NA, NA, .4, .3),
                          ncol = 4)
colnames(horizontal_view) <- c("2022Q1", "2022Q2", "2022Q3", "2022Q4")
rownames(horizontal_view) <- c("2022-07-31", "2022-08-31", "2022-09-30", "2022-10-31",
                               "2022-11-30", "2022-12-31", "2023-01-31", "2023-02-28")
print(horizontal_view)

# Vertical format
vertical_view <- matrix(data = c(.8, .2, NA, NA, .8, .1, NA, NA, .7, .1, NA,
                                 NA, .7, .2, .5, NA, .7, .2, .5, NA, .7, .3, .7, NA,
                                 .7, .2, .7, .4, .7, .3, .7, .3),
                        nrow = 4)
rownames(vertical_view) <- c("2022Q1", "2022Q2", "2022Q3", "2022Q4")
colnames(vertical_view) <- c("2022-07-31", "2022-08-31", "2022-09-30", "2022-10-31",
                             "2022-11-30", "2022-12-31", "2023-01-31", "2023-02-28")
print(vertical_view)
```

## Processing

```{r loading package, echo = TRUE, eval = TRUE}
library("rjd3revisions")
```

Once your input data are in the right format, you create the vintages:

```{r create vintage, echo = TRUE, eval = TRUE}
vintages <- create_vintages(long_view, type = "long", periodicity = 4L)
# vintages <- create_vintages_from_xlsx(
#     file = "myinput.xlsx",
#     type = "long",
#     periodicity = 4,
#     "Sheet1"
# )
# vintages <- create_vintages_from_csv(
#     file = "myinput.csv",
#     periodicity = 4,
#     sep = "\t",
#     date_format = "%Y-%m-%d"
# )

print(vintages) # extract of the vintages according to the different views
summary(vintages) # metadata about vintages
```

possibly inspect the revisions and perform the revision analysis:

```{r revision analysis, echo = TRUE, eval = FALSE}
revisions <- get_revisions(vintages, gap = 1)

plot(revisions)

print(revisions) # extract of the revisions according to the different views
summary(revisions) # metadata about revisions
```

Finally to create the report and get a summary of the results, you can use the function `revision_analysis`{.r}

```{r create report, echo = TRUE, eval = TRUE}
rslt <- revision_analysis(vintages, gap = 1, view = "diagonal", n.releases = 3)

summary(rslt)
print(rslt)
```

To export the report in pdf or html format, you can use the function `render_report`{.r}

```{r export report, echo = TRUE, eval = FALSE}
render_report(
    rslt,
    output_file = "my_report",
    output_dir = "C:/Users/xxx",
    output_format = "pdf_document"
)
```

## Details on the main functions

### Vintages & revisions {#vintages}

Once your input data are in the right format, you must first create an object of the class `rjd3rev_vintages` before you can run your revision analysis. The function `create_vintages()` (or, alternatively, `create_vintages_from_xlsx()` or `create_vintages_from_csv()`) will create this object from the input data and display the vintages considering three different data structures or views: vertical, horizontal and diagonal.

1. The **vertical view** shows the observed values at each time period by the different vintages. This approach is robust to changes of base year and data redefinition and could for example be used to analyse revisions resulting from a benchmark revision. A drawback of this approach is that for comparing the same historical series for different vintages, we need to look at the smallest common number of observations and consequently the number of observations is in some circumstances very small. Moreover, it is often the case that most of the revision is about the last few points of the series so that the number of observations is too small to test anything.

| Period   | 2023/03/31 | 2023/04/30 | 2023/05/31 |
| -------- | ---------- | ---------- | ---------- |
| 2022M01  | 15.2       | 15.1       | 15.0       |
| 2022M02  | 15.0       | 14.9       | 14.9       |
| ...      | ...        | ...        | ...        |
| 2023M01  | 13.0       | 13.1       | 13.2       |
| 2023M02  |            | 12.1       | 12.1       |
| 2023M03  |            |            | 12.3       |

Table: Example of vertical view

2. The **horizontal view** shows the observed values of the different vintages by the period. A quick analysis can be performed by rows in order to see how for the same data point (e.g. 2023Q1), figures are first estimated, then forecasted and finally revised. The main findings are usually obvious: in most cases the variance decreases, namely data converge towards the 'true value'. Horizontal tables are just a transpose of vertical tables and are not used in the tests in 'revision_analysis'.

| Period     | 2022M01 | 2022M02 | ...     | 2023M01 | 2023M02 | 2023M03 |
| ---------- | ------- | ------- | ------- | ------- | ------- | ------- |
| 2023/03/31 | 15.2    | 15.0    | ...     | 13.0    |         |         |
| 2023/04/30 | 15.1    | 14.9    | ...     | 13.1    | 12.1    |         |
| 2023/05/31 | 15.0    | 14.9    | ...     | 13.2    | 12.1    | 12.3    |

Table: Example of horizontal view

3. The **diagonal view** shows subsequent releases of a given time period, without regard for the date of publication. The advantage of the diagonal approach is that it gives a way to analyse the trade between the timing of the release and the accuracy of the published figures. It is particularly informative when regular estimation intervals exist for the data under study (as it is the case for most of the official statistics). However, this approach requires to be particularly vigilant in case there is a change in base year or data redefinition.

| Period   | Release1   | Release2   | Release3   |
| -------- | ---------- | ---------- | ---------- |
| 2023M01  | 13.0       | 13.1       | 13.2       |
| 2023M02  | 12.1       | 12.1       |            |
| 2023M03  | 12.3       |            |            |

Table: Example of diagonal view

Note that in the argument of the function `create_vintages()`, the argument `vintage_selection` allows you to limit the range of revision dates to consider if needed. See ?create_vintages for more details.

Revisions are easily calculated from vintages by choosing the gap to consider. The function `get_revisions()` will display the revisions according to each view. It is just an informative function that does not need to be run prior the revision analysis.

### Revision analysis & reporting

The function `revision_analysis()` is the main function of the package. It provides some descriptive statistics and performs a battery of parametric tests which enable the users to detect potential bias (both mean and regression bias) and sources of inefficiency in preliminary estimates. We would conclude to inefficiency in the preliminary estimates when revisions are predictable in some way. Parametric tests are divided into 5 categories: relevancy (check whether preliminary estimates are even worth it), bias, efficiency, orthogonality (correlation at higher lags), and signalVSnoise. This function is robust. If for some reasons, a test fails to process, it is just skipped and a warning is sent to users with the possible cause of failure. The other tests are then performed as usual.

For some of the parametric tests, prior transformation of the vintage data may be important to avoid misleading results. By default, the decision to differentiate the vintage data is performed automatically based on unit root and co-integration tests. More specifically, we focus on the augmented Dickey-Fuller (ADF) test to test the presence of unit root and, for cointegration, we proceed to an ADF test on the residuals of an OLS regression between the two vintages. The results of those tests are also made available in the output of the function (section 'varbased'). By contrast, the choice of log-transformation is left to the discretion of the users based on their knowledge of the series and the diagnostics of the various tests. By default, no log-transformation is considered.

As part of the arguments of the `revision_analysis()` function, you can choose the view and the gap to consider, restrict the number of releases under investigation when diagonal view is selected and/or change the default setting about the prior transformation of the data (including the possibility to add a prior log-transformation of your data).  

The function `render_report()` applied on the output of `revision_analysis()` will generate an enhanced HTML report including both a formatted summary of the results and full explanations about each test (which are also included in the vignette below). The formatted summary of the results display the p-value of each test (except for Theil's tests where the value of the statistics is provided) and their interpretation. An appreciation 'good', 'uncertain', 'bad' and 'severe' is indeed associated to each test following the usual statistical interpretation of p-values and the orientation of the tests. This allows a quick visual interpretation of the results and is similar to what is done in the GUI of JDemetra+. 

In addition to the function `revision_analysis()`, the user can also perform tests individually if they want to. To list all functions available in the package (and therefore finding the different functions corresponding to the individual tests), you can do

```{r, echo = TRUE, eval = TRUE}
ls("package:rjd3revisions")
```

Use help(‘name of the functions’) or ?‘name of the functions’ for more information and examples over the various functions.

## Output

The detailed results of each test are part of the output returned by the function `revision_analysis()`. Alternatively, the functions associated with the individual test will give you the same result specific to this test. 

In addition to the visual report that you can get by applying the function `render_report()` on the output of the function `revision_analysis()`, you can also apply the usual `summary()` and `print()` functions to this output. The function `summary()`, in particular, will print only the formatted table of the report with the main results. The `print()` will provide the same unformatted information together with some extra ones. Finally the `plot()` function applied to the output of the function `get_revisions()` will provide you with a visual of the revisions over time.

# Tests description and interpretation

Recall that the purpose of the parametric tests described below are:

- To check the *relevancy* of preliminary estimates
- To detect potential mean and regression *bias*  
- To measure *efficiency* of preliminary estimates (i.e., whether revisions are somehow predictable)

## Relevancy

### Theil’s Inequality Coefficient

In the context of revision analysis, Theil's inequality coefficient, also known as Theil's U, provides a measure of the accuracy of a set of preliminary estimates (P) compared to a latter version (L). There exists a few definitions of Theil's statistics leading to different interpretation of the results. In this package, two definitions are considered. The first statistic, U1, is given by
$$
U_1=\frac{\sqrt{\frac{1}{n}\sum^n_{t=1}(L_t-P_t)^2}}{\sqrt{\frac{1}{n}\sum^n_{t=1}L_t^2}+\sqrt{\frac{1}{n}\sum^n_{t=1}P_t^2}} \\ \\
$$
U1 is bounded between 0 and 1. The closer the value of U1 is to zero, the better the forecast method. However, this classic definition of Theil's statistic suffers from a number of limitations. In particular, a set of near zero preliminary estimates would always give a value of the U1 statistic close to 1 even though they are close to the latter estimates.

The second statistic, U2, is given by
$$
U_2=\frac{\sqrt{\sum^n_{t=1}\left(\frac{P_{t + 1}-L_{t + 1}}{L_t}\right)^2}}{\sqrt{\sum^n_{t=1}\left(\frac{L_{t + 1}-L_t}{L_t}\right)^2}}
$$
The interpretation of U2 differs from U1. The value of 1 is no longer the upper bound of the statistic but a threshold above (below) which the preliminary estimates is less (more) accurate than the naïve random walk forecast repeating the last observed value (considering $P_{t + 1}=L_t$). Whenever it can be calculated ($L_t \neq 0 ~\forall t$), the U2 statistic is the preferred option to evaluate the relevancy of the preliminary estimates.


## Bias

A bias in preliminary estimates may indicate inaccurate initial data or inefficient compilation methods. However, we must be cautious if a bias is shown to be statistically significant and we intend to correct it. Biases may change overtime, so we might correct for errors that no longer apply. Over a long interval, changes in methodology or definitions may also occur so that there are valid reasons to expect a non-zero mean revision.

### T-test and Augmented T-test

To test whether the mean revision is statistically different from zero for a sample of n, we employ a conventional t-statistic
$$
t=\frac{\overline{R}}{\sqrt{s^2/n}}
$$
If the null hypothesis that the bias is equal to zero is rejected, it may give an insight of whether a bias exists in the earlier estimates. 

The t-test is equivalent to fitting a linear regression of the revisions on only a constant (i.e. the mean). Assumptions such as the gaussianity of the revisions are implied. One can release the assumption of no autocorrelation by adding it into the model. Hence we have
$$
R_t=\mu+\varepsilon_t, ~~t=1,...,n
$$
And the errors are thought to be serially correlated according to an AR(1) model, that is
$$
\varepsilon_t=\gamma\varepsilon_t+u_t, ~~with~ |\gamma|<1 ~and ~u_t \sim{iid} 
$$
The auto-correlation in the error terms reduces the number of independent observations (and the degrees of freedom) by a factor of $n\frac{(1-\gamma)}{(1+\gamma)}$ and thus, the variance of the mean should be adjusted upward accordingly.

Hence, the Augmented t-test is calculated as
$$
t_{adj}=\frac{\overline{R}}{\sqrt{\frac{s^2(1+\hat{\gamma})}{n(1-\hat{\gamma})}}}
$$
where
$$
\hat{\gamma}=\frac{\sum^{n-1}_{t=1}(R_t-\overline{R})(R_{t + 1}-\overline{R})}{\sum^n_{t=1}(R_t-\overline{R})^2}
$$

### Slope and drift

We assume a linear regression model of a latter vintage (L) on a preliminary vintage (P) and estimate the intercept (drift) $\beta_0$ and slope coefficient $\beta_1$ by OLS. The model is

$$
L_t=\beta_0+\beta_1P_t+\varepsilon_t
$$
While the (augmented) t-test on revisions only gives information about mean bias, this regression enables to assess both mean and regression bias. A regression bias would occur, for example, if preliminary estimates tend to be too low when latter estimates are relatively high and too high when latter estimates are relatively low. In this case, this may result in a positive value of the intercept and a value of $\beta_1<1$. To evaluate whether a mean or regression bias is present, we employ a conventional t-test on the parameters with the null hypothesis $\beta_0 = 0$ and $\beta_1 = 1$.  

Recall that OLS regressions always come along with rather strict assumptions. Users should check the diagnostics and draw the necessary conclusions from them. 

## Efficiency

Efficiency tests evaluate whether preliminary estimates are "efficient" forecast of the latter estimates. If all information were used efficiently at the time of the preliminary estimate, revisions should not be predictable and therefore neither be correlated with preliminary estimates or display any relationship from one vintage to another. This section focuses on these two points. Predictability of revisions is tested even further in the Orthogonality and SignalVSNoise sections.

### Regression of revisions on previous estimates

We assume a linear regression model of the revisions (R) on a preliminary vintage (P) and estimate the intercept $\beta_0$ and slope coefficient $\beta_1$ by OLS. The model is

$$
R_t=\beta_0+\beta_1P_t+\varepsilon_t, ~~t=1,...,n
$$
If revisions are affected by preliminary estimates, it means that those are not efficient and could be improved. We employ a conventional t-test on the parameters with the null hypothesis $\beta_0 = 0$ and $\beta_1 = 0$. Diagnostics on the residuals should be verified.

### Regression of revisions from latter vintages on revisions from the previous vintages

We assume a linear regression model of the revisions between latter vintages ($R_v$) on the revisions between the previous vintages ($R_{v-1}$) and estimate the intercept $\beta_0$ and slope coefficient $\beta_1$ by OLS. The model is

$$
R_{v,t}=\beta_0+\beta_1R_{v-1,t}+\varepsilon_t, ~~t=1,...,n
$$
If latter revisions are predictable from previous revisions, it means that preliminary estimates are not efficient and could be improved. We employ a conventional t-test on the parameters with the null hypothesis $\beta_0 = 0$ and $\beta_1 = 0$. Diagnostics on the residuals should be verified.


## Orthogonality

Orthogonality tests evaluate whether revisions from older vintages affect the latter revisions. This section also includes autocorrelation and seasonality tests for a given set of revisions. If there is significant correlation in the revisions for subsequent periods, this may witness some degree of predictability in the revision process.          

### Regression of latter revisions (Rv) on previous revisions (Rv_1, Rv_2,...Rv_p)

We assume a linear regression model of the revisions from latter vintages ($R_v$) on the revisions from p previous vintages ($R_{v-1}, ..., R_{v-p}$) and estimate the intercept $\beta_0$ and slope coefficients of $\beta_1, ..., \beta_p$ by OLS. The model is

$$
R_{v,t}=\beta_0+\sum^p_{i=1}\beta_{i}R_{v-i,t}+\varepsilon_t, ~~t=1,...,n
$$
If latter revisions are predictable from previous revisions, it means that preliminary estimates are not efficient and could be improved. We employ a conventional t-test on the intercept parameter with the null hypothesis $\beta_0 = 0$ and a F-test to check the null hypothesis that $\beta_1 = \beta_2=...=\beta_p=0$. Diagnostics on the residuals should be verified

### Regression of latter revisions (Rv) on revisions from a specific vintage (Rv_k)

We assume a linear regression model of the revisions from latter vintages ($R_v$) on the revisions from a specific vintage ($R_{v-k}$) and estimate the intercept $\beta_0$ and slope coefficient $\beta_1$ by OLS. The model is

$$
R_{v,t}=\beta_0+\beta_1R_{v-k,t}+\varepsilon_t, ~~t=1,...,n
$$
If latter revisions are predictable from previous revisions, it means that preliminary estimates are not efficient and could be improved. We employ a conventional t-test on the parameters with the null hypothesis $\beta_0 = 0$ and $\beta_1 = 0$. Diagnostics on the residuals should be verified.

### Test of autocorrelations in revisions 

To test whether autocorrelation is present in revisions, we employ the Ljung-Box test. The Ljung-Box test considers together a group of autocorrelation coefficients up to a certain lag k and is therefore sometimes referred to as a portmanteau test. For the purpose of revision analysis, as we expect a relatively small number of observations, we decided to restrict the number of lags considered to $k=2$. Hence, the users can also make the distinction with autocorrelation at seasonal lags (see seasonality tests below).     

The null hypothesis is no autocorrelation. The test statistic is given by
$$
Q=n(n+2)\sum^k_{i=1}\frac{\hat{\rho}_i^2}{n-i}
$$
where n is the sample size, $\hat{\rho}_i^2$ is the sample autocorrelation at lag in and $k=2$ is the number of lags being tested. Under the null hypothesis, $Q\sim\chi^2(k)$.

If Q is statistically different from zero, the revision process may be locally biased in the sense that latter revisions are related to the previous ones. 

### Test of seasonality in revisions

To test whether seasonality is present in revisions, we employ two tests: the parametric QS test and the non-parametric Friedman test. Note that seasonality tests are always performed on first-differentiated series to avoid misleading results.

The QS test is a variant of the Ljung-Box test computed on seasonal lags, where we only consider positive auto-correlations
$$
QS=n(n+2)\sum^k_{i=1}\frac{\left[max(0,\hat{\gamma}_{i.l})\right]^2}{n-i.l}
$$
where $k=2$, so only the first and second seasonal lags are considered. Thus, the test would checks the correlation between the actual observation and the observations lagged by one and two years. Note that $l=12$ when dealing with monthly observations, so we consider the auto-covariances $\hat{\gamma}_{12}$ and $\hat{\gamma}_{24}$ alone. In turn $k=4$ in the case of quarterly data.

Under the null hypothesis of no autocorrelation at seasonal lags, $QS\sim \chi_{modified}^2(k)$. The elimination of negative correlations calls indeed for a modified $\chi^2$ distribution. This was done using simulation techniques.

The Friedman test requires no distributional assumptions. It uses the rankings of the observations. It is constructed as follows. Consider first the matrix of data $\{x_{ij}\}_{nxk}$ with n rows (the blocks, i.e. the number of years in the sample), k columns (the treatments, i.e., either 12 months or 4 quarters, depending on the frequency of the data). The data matrix needs to be replaced by a new matrix $\{r_{ij}\}_{nxk}$, where the entry $r_{ij}$ is the rank of $x_{ij}$ within the block i. The test statistic is given by

$$
Q=\frac{n\sum^k_{j=1}(\tilde{r}_{.j}-\tilde{r})^2}{\frac{1}{n(k-1)}\sum^n_{i=1}\sum^k_{j=1}(r_{ij}-\tilde{r})^2}
$$
The denominator represents the variance of the average ranking across treatments j relative to the total. Under the null hypothesis of no (stable) seasonality, $Q\sim \chi^2(k-1)$.

As for non-seasonal autocorrelation tests at lower lags, if QS and Q are significantly different from zero, the revision process may be locally biased in the sense that latter revisions are related to the previous ones.


## Signal vs Noise

Regression techniques can also be used to determine whether revisions should be classified as ‘news’ or ‘noise’. Those are also closely related to the notion of efficiency developed earlier. 

If the correlation between revisions and preliminary estimates is significantly different from zero, this implies that we did not fully utilize all the information available at the time of the preliminary estimates. In that sense, we would conclude that the preliminary estimates could have been better and that revisions embody noise. The model to test whether revisions are "noise" is similar to the first model established earlier to test efficiency: 
$$
R_t=\beta_0+\beta_1P_t+\varepsilon_t, ~~t=1,...,n
$$
We employ a F-test on the parameters to test jointly that $\beta_0 = 0$ and $\beta_1 = 0$. If the null hypothesis is rejected, this suggest that revisions are likely to include noise. Diagnostics on the residuals should be verified.

On the other hand, revisions should be correlated to the latter estimates. If this is the case, it means that information which becomes
available between the compilation of the preliminary and the latter estimates are captured in the estimation process of the latter estimates. In that sense, the revision process is warranted and we conclude that revisions embody news. The model to test whether revisions are "news" is

$$
R_t=\beta_0+\beta_1L_t+\varepsilon_t, ~~t=1,...,n
$$
We employ a F-test on the parameters to test jointly that $\beta_0 = 0$ and $\beta_1 = 0$. If the null hypothesis is rejected, this is a good thing as it suggests that revisions incorporate news. Note that even if we reject the null hypothesis and conclude that revisions incorporate news, it does not necessarily mean that revisions are efficient as those might still be predicted by other variables not included in the estimation process.

# References

- Ares, David. 2013. “Tool for Revision Analysis : Technical Report.” DI/06769. DG ESTAT.
- Cook, Steve. 2019. “Forecast Evaluation Using Theil’s Inequality Coefficients.” Swansea University; https://www.economicsnetwork.ac.uk/showcase/cook_theil.
- Fixler, Dennis. 2007. “How to Interpret Whether Revisions to Economic Variables Reflect ‘News’ or ‘Noise’.” OECD.
- McKenzie, Richard, and Michela Gamba. 2007. “Interpreting the Results of Revision Analyses: Recommended Summary Statistics.” OECD.
- Pitton, Laurent, and David Ares. 2013a. “Tool for Revision Analysis : Regression Based Parametric Analysis.” DI/06769. DG ESTAT.
- Pitton, Laurent, and David Ares. 2013b. “Tool for Revision Analysis : VAR Based Models and Final Equation.” DI/06769. DG ESTAT.
- Smyk, Anna, Tanguy Barthelemy, Karsten Webel and al. 2024. “JDemetra+ Documentation.” INSEE; https://jdemetra-new-documentation.netlify.app/.

